Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-25 proposal/prop.tex
prop.tex \section{Overview, Objectives, and Expected Significance} Cite Meyer-Mermin...

We will begin by reviewing existing work that recasts classical
probability spaces in a resource-aware setting and move to our
proposal which, briefly speaking, aims at recasting quantum
probability and hence quantum measurement to a corresponding
resource-aware setting. In particular, we plan on addressing the
Meyer-Mermin debate~\cite{} on the impact of finite precision
measurements on the relevance of the Kochen-Specker theorem. We argue
that no matter what the results are their impact will be
strong. Positive results that formulate a computable, with clear
resource bounds, theory of quantum measurement and quantum probability
would be essential for understanding and realizing quantum
computation. Any negative results would redirect research that aims at
realizing quantum computation to other approaches. At an intellectual
level, the results will solve or clarify several paradoxes in quantum
mechanics, quantum information, computability, and complexity theory.

>>>>

We will begin by reviewing existing work that recasts classical
probability spaces in a resource-aware setting and move to our
proposal which, briefly speaking, aims at recasting quantum
probability and hence quantum measurement to a corresponding
resource-aware setting. In particular, we plan on addressing the
Meyer-Mermin debate~\cite{PhysRevLett.83.3751, Mermin1999, BarrettKent2004}
on the impact of finite precision
measurements on the relevance of the Kochen-Specker theorem. We argue
that no matter what the results are their impact will be
strong. Positive results that formulate a computable, with clear
resource bounds, theory of quantum measurement and quantum probability
would be essential for understanding and realizing quantum
computation. Any negative results would redirect research that aims at
realizing quantum computation to other approaches. At an intellectual
level, the results will solve or clarify several paradoxes in quantum
mechanics, quantum information, computability, and complexity theory.
